\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-01 evaluation.tex
update in table
some restracturing to emphasize the case studies early on
MigratingTable: description of bug 3

\setlength{\tabcolsep}{.42em}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rr rrrrr}
\centering
\input{experiments/tables/results.tex}
\end{tabular}
\caption{Results.}
\label{tab:testing}
\end{table*}

@@

>>>>

\setlength{\tabcolsep}{.42em}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rr rrrr}
\centering
\input{experiments/tables/results.tex}
\end{tabular}
\caption{Results from 100000 iterations of \psharp random walk scheduler.}
\label{tab:testing}
\end{table*}

@@

\subsection{An example bug in MigratingTable}
\MMComment{Move wherever appropriate}

One of the bugs in MigratingTable that we found using the \psharp test stands out because it reflects the type of oversight that tends to occur as designs evolve and it's unclear whether we would have been able to find it by any other method (\MMComment{revise remark when we have stress test results?}).  This bug, which we named QueryStreamedBackUpNewStream, is in the implementation of a streaming read from the virtual table, which should return a stream of all rows in the table sorted by key.  The essential implementation idea is to start streams $s_O$, $s_N$ from the old and new backend tables and merge the sorted streams by keeping track of the next row in each stream and returning the row with the lesser key.  In parallel, the migrator job is concurrently copying rows from the old table to the new table; we had satisfied ourselves that this concurrency would not cause any problems.  However, then we added support to the migrator job to delete the old table when it finishes copying, which triggers the virtual stream to close $s_O$.  Suppose the virtual stream is in a state in which the next row in $s_O$ has key $k_O$ and the next row in $s_N$ has key $k_N$, where $k_O < k_N$.  Further suppose that before the next read from the virtual stream, the migrator job copies a row with key $k$ ($k_O < k < k_N$) from the old table to the new table and then deletes the old table.  Since $s_O$ has not yet returned this row when it is closed and $s_N$ has already advanced to $k_N$, the row with key $k$ will be missed by the virtual stream.  A similar problem can occur if $s_N$ does not reflect rows inserted into the new table by the migrator job after $s_N$ is started, as allowed by the IChainTable2 specification.  Restarting $s_N$ when the old table is deleted fixes both variants of the bug.

\MMComment{Add a figure based on migration-bug3-explanation.pptx (probably a hybrid of slides 4 and 5, assuming we want only one figure).}
